Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
stuff

Re-Cleaned 
```{r} 
google <- google %>%  select(-c(X.1))
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(as.Date(Day))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))

@@

```{r}
## Positive COVID cases map before and after week 
plot3<-statebins(state_data = weekbefore, state_col = "State",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =7,
                     legend_title="Week Before",
                 labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))

### Drastic scale change, needs work for comparison sake
plot4<-statebins(state_data = weekafter, state_col = "state",
                     text_color = "white", value_col = "positive",
                     brewer_pal="Spectral", font_size = 3,breaks =6,
                     legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))

plot3
plot4
```

@@

```{r}
set.seed(84735)
test1 <- Finaldata %>% 
  select(mean_KungFluInterest, percent_republican2016, percent_asian, StateColor) %>%
  na.omit() %>% 
  sample_n(500)

names(test1) <- tolower(names(test1))

test1
```

```{r}
set.seed(454)
building_mod <- stan_glm(
  mean_kungfluinterest ~ percent_republican2016 + percent_asian +statecolor, 
  data = test1, 
  family = gaussian, 
  chains = 4, iter = 10000
)
```

```{r}
mcmc_trace(building_mod)
mcmc_dens_overlay(building_mod)
```

```{r}
pp_check(building_mod)

# Could build like the sleep study, 50 frames one for each state and how Google Trends changed over time, each state has its own trajectory
# Can we look at each state and how their interest changes over time and if that's related to how many cases are in the state

#What's the trend in interest and how does it depend on cases? 
```

```{r}
summary_building_mod <- summary(building_mod)

head(as.data.frame(summary_building_mod),-2)
```

```{r, include=FALSE}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}

prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # This function summarizes the predictions across all cases
  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
    mutate(error = y - post_median) %>% 
    mutate(error_scaled = error / post_mad) %>% 
    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
    mutate(within_outer = (y >= l_outer) & (y <= u_outer))

  pred_summary <- pred_data %>% 
    summarize(mae = median(abs(error)), 
      mae_scaled = median(abs(error_scaled)),
      within_inner = mean(within_inner),
      within_outer = mean(within_outer)
    )
  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
  names(pred_summary)[4] <- paste0("within_", prob_outer*100)

  pred_summary
}
```

```{r}
preds <- posterior_predict(building_mod,newdata = test1) # Ask Alicia 
prediction_summary(y = test1$mean_kungfluinterest, yprep = preds)

```

>>>>

Re-Cleaned 
```{r} 
google <- google %>%  select(-c(X.1))
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.Date("2020-03-17"))

@@

```{r}
# ## Positive COVID cases map before and after week 
# plot3<-statebins(state_data = weekbefore, state_col = "State",
#                      text_color = "white", value_col = "positive",
#                      brewer_pal="Spectral", font_size = 3,breaks =7,
#                      legend_title="Week Before",
#                  labels = c("0","1-5","5-10","10-20","20-30","30-40","50-100"))
# 
# ### Drastic scale change, needs work for comparison sake
# plot4<-statebins(state_data = weekafter, state_col = "state",
#                      text_color = "white", value_col = "positive",
#                      brewer_pal="Spectral", font_size = 3,breaks =6,
#                      legend_title="Week After",labels = c("1-100", "100-500", "500-5000", "5000-15000", "15000-25000", "25000-35000"))
# 
# plot3
# plot4
```

@@
